---
title: "Prediction Assignment Writeup"
author: "Mashael Alonaizan"
date: "11/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive summary
The goal of this project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 
we will build prediction model to predict this. 

## Analysis

First, we need to laod the library needed in prediction: 

```{r, echo=FALSE}
library(knitr)
library(caret)
library(lattice)
library(ggplot2)
library(rpart)
library(rpart.plot)
```
then, we start to explore and clean the data and remove null values. 

```{r, echo=FALSE}
training_data <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"))
testing_data <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"))
intraining<-createDataPartition(y=training_data$classe,p=0.75,list=FALSE)
training_set<-training_data[intraining,]
testing_set<-training_data[-intraining,]
near_zero<- nearZeroVar(training_set)
training_set<-training_set[,-near_zero]
testing_set<-testing_set[,-near_zero]
Null_vales<-sapply(training_set, function(x) mean(is.na(x))) > 0.95
training_set<-training_set[,Null_vales== FALSE]
testing_set <-testing_set[,Null_vales== FALSE]
training_set<-training_set[,-(1:5)]
testing_set <-testing_set[,-(1:5)]
modelFit <- train(classe ~ ., data=training_set, method='rf', verbose=T, na.action=na.exclude)

```
here we build a random forest model by train the data

```{r, echo=FALSE}
set.seed(1000)
modelFit <- train(classe ~., data=training_set, method='rf', trControl=trainControl(method="cv",number=3))
modelFit
```
then, we predict a new sample  

```{r echo=FALSE}
predictions<-predict(modelFit,testing_set)
predictions
```
 then, we using confusion matrix to see the performance.  
```{r}
confusionMatrix(predictions,testing_set$classe)
```

finally, we predict the classe output by using test sample data: 
```{r}
testing_data_2 <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"))
Final_prediction<-predict(modelFit,testing_data_2)
print(Final_prediction)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
